Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-01-28 WSSSPE1_report/WSSSPE1_summary_report.tex

\section{Agenda}

@@

>>>>

\section{Agenda}
The workshop submissions were classified into various related categories.
Representatives from each submission categories were appointed as penalists. The sessions were kickstarted with keynote talks followed by panel discussions.

@@

Arfon Smith of github presented the first keynote. Following points summarize the keynote and the associated discussion:
\begin{enumerate}
    \item Socially driven software development.
    \item Role of software in research.
\end{enumerate}
